---
# YAML header ----
# qmd yaml chunk (note the 3 x '-' at the begining and end of the chunk)
# description: 
#  Use the yaml to:
#   - control document metadata-files: e.g., title, subtitle, description, abstract, date, bibliography.
#   - set document formating: e.g. document output type (html, docx, pdf, pptx), table of contents (toc), html behavior.
#       - For html see more here: https://quarto.org/docs/output-formats/html-basics.html
#       - For html see more here: https://quarto.org/docs/output-formats/pdf-basics.html
#       - For html see more here: https://quarto.org/docs/output-formats/ms-word.html
#   - html style can be handled by external style file (e.g. data_dev.css).
#   - If you want to force a line-break in the yaml use html '<br>'.
#   - Tabs (or spaces) and important in the yml (and main text). Indentation signals a sub option (or section).
# COMMENT = #

## Document metadata ----
title: "Scientific Services, BSPI Project report"
subtitle: "Project title"
author: "Name and Surname"
date: last-modified
date-format: "YYYY-MM-DD"
abstract: "Use this file as a project documentation template. <br> Insert here a sentence or two describing the project. List the 'umbrella' project that this report falls under where relevant. <br> "

## Document style ----
### html style ----
title-block-banner: true
format: 
    html:
        embed-resources: true
        smooth-scroll: true
        theme:
            - .ekznw_quarto/style/_ekznw_theme.scss
        fontcolor: black
        toc: true
        toc-location: left
        toc-title: Summary
        toc-depth: 3
        number-sections: true

### pdf style and options ----
    pdf:
        toc: true     # appears as a PDF ToC page
        number-sections: true

### Word document stype and options ----
    docx:
        number-sections: true
css: .ekznw_quarto/style/default_overrides.css

# Select bibliography ----
#  Cite with citation key like @cite_key or [@cite_key] for citations without,
# or within parentheses, respectively.
#  References will be printed in full at the end of the document.
bibliography: bspi.bib  # the source bib file can be downloaded from here:
                        # https://github.com/ekznw/refs
---

```{=html}
<!-- Quarto cheatsheet: https://rstudio.github.io/cheatsheets/quarto.pdf

In the Quarto main document wherein the write-up can be meshed with code. You can insert markdown comments that are not rendered into html, word etc using a 'markdown' block — note the beginning and end 3 x ` characters. This sequence of special characters in Quarto tell the renderer that this is special section, particularly, a comment section.   
See https://quarto.org/docs/authoring/callouts.html for more on callout blocks. There is a callout 'tip' box below. -->
```

::: {.callout-tip title="NB!"}
The contents of this report should enable replication or further development of the project and associated data products.
:::

# Revision history

::: {.callout-tip title="Tip"}
Remove contents for this project report template info below; then, for your project, add rows for major revisions or comments. Follow *version convention*: pre-release = v0.1 – v0.9; release \> v0.9.
:::

::: {#tbl-rev}
| Date | Person(s) | Note | Version |
|:----------------|:----------------|:---------------------|:----------------|
| 2026-02-09 | Paul Gordijn | Draft project workflow document for comment. | v0.2 |
| 2026-05-05 | Paul Gordijn | Updated style references and BibTeX. | v0.3 |

Project documentation revision history and version number.
:::

# Project summary

Now I can edit in visual mode...

## Purpose

::: {.callout-tip title="What to write"}
A note on the 'why' of the project.
:::

# Main steps

::: {.callout-tip title="What to write"}
List the main steps of the project. Keep it to the point—elaborate under 'Data processing' below.
:::

## First step (e.g. data prep)

## Other main processing steps

## ...

# Datasets used

::: {.callout-tip title="What to write"}
Dataset citation(s) from BibTeX or other citation database.
:::

- @nasajpl2021nmd
- @ekw2015km3
- @hawker2022a3m

# Data processing

::: {.callout-tip title="What to write"}
Detailed elaboration of the 'main steps'. Should enable full reproduction of the project.
:::

## First step (e.g. data prep)

We made up some data.

```{r}
df <- data.frame(
    a = 1:5,
    b = rep(1, 5),
    c = c("a", "b", "c", "d", "e")
)
```

```         
a. Sub-item ...
a.
a.
```

We checked out the data structure.

```{r}
str(df)
```

## Other main processing steps

We estimated the mean of 'a'.

```{r}
mean(df$a)
```

Our options presented for data processing (*see* @tbl-mytable below).

::: {#tbl-mytable}
| Options     | Reasoning                            |
|-------------|--------------------------------------|
| Option one. | Go with 'a' as it has a mean of 3.   |
| Option two  | Perhaps we should estimate variance. |

Options table.
:::

## ...

# Products

::: {.callout-tip title="What to write"}
Notes on the final report and associated products.
:::

## Conclusion

::: {.callout-tip title="What to write"}
Concluding remarks.
:::

# Appendices

## Appendix A: metadata

::: {.callout-tip title="What to write"}
More on this to come...
:::

## Appendix B: supporting documentation

::: {.callout-tip title="What to write"}
List supporting documentation if it needs to be highlighted.
:::

## Appendix C: Project folder structure

```         
├── 📁 data         | Data folder
│   ├── 📁 arc      | Folder for archived data.
│   ├── 📁 dev      | Folder for datasets in development & temp files.
│   └── 📁 src      | Externally sourced data.
├── 📁 images       | Miscellaneous images.
│   └── 🖼️ graph01.png | Misc figs etc
├── 📁 .ekznw_quarto                  | Quarto document style
│   ├── 🎨 _ekznw_theme.scss          | Html theme.
│   ├── 🎨 default_overrides.css
├── 🌐 data_dev.html | Rendered html output
└── 📄 data_dev.qmd  | Raw Quarto document
```

## Appendix D: Processing environment

### R environment

```{r}
#| eval: true
sessionInfo()
```

# References (example references)